
# aframer

```{r, eval=TRUE, include=FALSE}
library(htmltools)
```

```{r, echo=FALSE}
div(
  class = "row",
  div(
    class = "col-md-3",
    img(src = "logo.png")
  ),
  div(
    class = "col-md-9",
    p(
      "Make Web Virtual Reality in R."
    ),
    p(
      a(
        href = "https://arframer.john-coene.com/",
        target = "_blank",
        class = "btn btn-lg btn-primary btn-blue",
        tags$i(
          class = "fa fa-camera"
        ),
        "Augmented Reality"
      )
    )
  )
)
```

#### Installation

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/aframer")
```

You can install `aframer`, all its [packages](articles/packages.html) and [components](articles/components.html) with `vrrr`, **V**irtual **R**itual in **R** (with another **R**).

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/vrrr")
```

#### Example

1. You can browse by encapsulating `a_scene` in `browse_aframe`.
2. Embed the visualisation in R markdown with `embed_aframe`.
3. Serve visualisations with `serve_aframe`.

```{r}
library(aframer)

embed_aframe(
  a_scene(
    a_dependency(),
    a_box(
      position = "-1 0.5 -3", rotation = "0 45 0", color = "#4CC3D9"
    ),
    a_sphere(
      position = "0 1.25 -5", radius = "1.25", color = "#EF2D5E"
    ),
    a_cylinder(
      position = "1 0.75 -3", radius = "0.5", height = "1.5", color = "#FFC65D"
    ),
    a_plane(
      position = "0 0 -4", rotation = "-90 0 0", width = "4", height = "4", color = "#7BC8A4"
    ),
    a_sky(
      color="#ECECEC"
    )
  )
)
```

```{r, echo=FALSE}
br()
```

Click the button below to view the full screen output of the code above.

```{r, echo=FALSE}
tags$a(
  tags$i(class = "fa fa-lg fa-eye"),
  " Demo",
  href = "example.html",
  target = "_blank",
  class = "btn btn-lg btn-primary"
)
```
